Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training with GPUs

### 2020-12-26 NEUROC/sec4-experiments.tex
grammer和修正了sec4.4的语法

The sample-based inference was an effective technique to handle big graphs.
%
Taking the node classification task as an example, to predict labels for a given set of vertices $\mathcal{V}_{predict}$, the inference sampler sampled a subgraph containing complete $L$-hop neighborhoods of all vertices in $\mathcal{V}_{predict}$, where $L$ was the number of GNN layers.
%
Since the real-world graphs often had small-world property, the size of the sampled subgraph increased quickly as the number of vertices in $\mathcal{V}_{predict}$ (i.e., batch size) increased.
%
Figure~\ref{fig:sampled_graph_size} (Figure X in the revised manuscript) shows how the relative batch size ($\frac{|\mathcal{V}_{predict}|}{|\mathcal{V}|}$) affected the average degree and the number of edges of the sampled subgraphs during inference.
%
When the relative batch size was 10\%, the number of edges in the sampled subgraphs were close to the number of edges in the whole graph in most datasets.
%
To limit the memory usage during inference, the batch size used should be very small.

@@

The relationships between batch size and test accuracy were complex.
%
A larger batch size did not always bring higher accuracy.
%
For example, the accuracy of GaAN in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amp} and GGNN in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_fli} decreased as the batch size increased.
%
A smaller batch size sometimes could achieve higher accuracy.
%
For example, GAT achieved a higher accuracy with 1\% relative batch size than the full-batch training in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amc}.
%
Given a sampling method, we found that the optimal batch size highly depended on the dataset and the GNN algorithm.
%
Our observations were similar to \cite{zeng2020_graphsaint}.
%
How to automatically select a proper batch size was a topic worth further studying.

>>>>

The sample-based inference was an effective technique to handle big graphs.
%
Taking the node classification task as an example, to predict labels for a given set of vertices $\mathcal{V}_{predict}$, the inference sampler sampled a subgraph containing complete $L$-hop neighborhoods of all vertices in $\mathcal{V}_{predict}$, where $L$ was the number of GNN layers.
%
Since the real-world graphs often had small-world property, the size of the sampled subgraph increased quickly as the number of vertices in $\mathcal{V}_{predict}$ (i.e., batch size) increased.
%
Figure~\ref{fig:sampled_graph_size} shows how the relative batch size ($\frac{|\mathcal{V}_{predict}|}{|\mathcal{V}|}$) affected the average degree and the number of edges of the sampled subgraphs during inference.
%
When the relative batch size was 10\%, the number of edges in the sampled subgraphs were close to the number of edges in the whole graph in most datasets.
%
To limit the memory usage during inference, the batch size used should be very small.

@@

The relationships between batch size and test accuracy were complex.
%
A larger batch size did not always bring higher accuracy.
%
For example, the accuracy of GaAN in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amp} and GGNN in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_fli} decreased as the batch size increased.
%
A smaller batch size sometimes could achieve higher accuracy.
%
For example, GAT achieved a higher accuracy with 1\% relative batch size than the full-batch training in \figurename~\ref{fig:exp_cluster_sampling_accuracy_on_amc}.
%
Given a sampling method, we found that the optimal batch size highly depended on the dataset and the GNN algorithm.
%
Our observations were similar to \cite{zeng2020_graphsaint}.
%
How to automatically select a proper batch size is a topic worth further studying.
